Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-25 vesicle_code/docs/adhesion/adhesion.tex
fixed up figure 1

\begin{figure}[htp]
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/configCartoon.pdf}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are 
  attractive.  {\em Right}: The resulting adhesive force of a single
  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
  point marked with a blue dot is repelled by the region of the vesicle
  denoted with a thick line, and attracted to the remainder of the
  vesicle.  The blue region is repelled to the right vesicle and the red
  region is attracted by the vesicle.}
\end{figure}

@@

Figure~\ref{fig:Dec18_vesicle_shape}(a) shows the equilibrium shapes of
vesicles with three values of reduced area: $\Delta A=0.95$, $0.75$ and
$0.6$ with $H=5$ \todo[inline]{Is this really the Hamaker constant?
It's not 0.5?} and $\delta = 0.2$.  The equilibrium vesicle shape for
$\Delta A=0.95$ is the circular cap with a flatten contact region.  This
is similar to the observed shapes of two vesicles under strong adhesive
interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.

@@

We investigate rheology of suspensions by computing the effective
viscosity of a doublet and compare it to the effective viscosity of a
single tank-treading vesicle. The effective viscosity is defined as the
viscosity of a homogeneous Newtonian fluid with the same energy
dissipation per macroscopic element of fluid.  In a simple shear flow,
the ambient velocity field is given by $\uu(\xx) = \chi(y,0)$, where
$\chi$ is the shear rate, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $\phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.
\todo[inline]{Stress $\sigma$ is also used for tension}

>>>>

\begin{figure}[htp]
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm]{figs/configCartoon.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are 
  attractive.  {\em Right}: The resulting adhesive force of a single
  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
  point marked with a blue dot is repelled by the region of the vesicle
  denoted with a thick line, and attracted to the remainder of the
  vesicle.  The blue region is repelled to the right vesicle and the red
  region is attracted by the vesicle.}
\end{figure}

@@

Figure~\ref{fig:Dec18_vesicle_shape}(a) shows the equilibrium shapes of
vesicles with three values of reduced area: $\Delta A=0.95$, $0.75$ and
$0.6$ with $H=5$ and $\delta = 0.2$.  The equilibrium vesicle shape for
$\Delta A=0.95$ is the circular cap with a flatten contact region.  This
is similar to the observed shapes of two vesicles under strong adhesive
interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.

@@

We investigate rheology of suspensions by computing the effective
viscosity of a doublet and compare it to the effective viscosity of a
single tank-treading vesicle. The effective viscosity is defined as the
viscosity of a homogeneous Newtonian fluid with the same energy
dissipation per macroscopic element of fluid.  In a simple shear flow,
the ambient velocity field is given by $\uu(\xx) = \chi(y,0)$, where
$\chi$ is the shear rate, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $\phi$ is the area fraction of
vesicles, $/tau$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.
